Reading Notes

### 2020-08-11 1summ.tex
pasted in NSF rubric as a guide

@@

>>>>

IM - Potential to advance knowledge and understanding within own and across different fields
    - Activities explore creative, original, or potentially transformative concepts?
    - Plan well-reasoned, well organized, based on sound rationale?
    - Mechanism to assess success?
    - How qualified is team?
    - Adequate resources to carry out activities?

@@

BI - Potential to benefit society, contribute to achievement of desired societal outcomes
    - Activities explore creative, original, or potentially transformative concepts?
    - Plan well-reasoned, well organized, based on sound rationale?
    - Mechanism to assess success?
    - How qualified is team?
    - Adequate resources to carry out activities?
